Predicting Sales Level for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-09 paper.tex
Added intro to Ensembles section

% You should say something before and after this. Why ensemble would
% work better, for instance - JJ

>>>>

The basic idea of ensemble classification is to train a set of base classifiers and then to combine their prediction using some combination scheme in a hope that the combined prediction will be better than the separated predictions. Empirically, ensemble learners tend to outperform their base members due to the significantly better generalization ability of the ensemble. This is because ensemble learners can reduce the the bias and variance problems of the base learning algorithms \cite{dietterich2002ensemble}. In the following, we describe the most popular ensemble methods: Bagging, Boosting and Random Forests.
